Alleviating Topology Mismatch in Distributed Overlay Networks: A Survey

### 2014-01-27 structured.tex
2012.10.24 (Vassilis) Changed paper title. Text reworked (content clarifications added, typos corrected, broken references fixed).

This section focuses on the structured P2P architectures. The following
paragraphs contain a thorough discussion and analysis of the algorithms proposed
in the literature for dealing with the topology mismatch problem in such
architectures. In structured P2P systems, the construction of the routing tables
in every participating node determines the efficiency of message forwarding.
Therefore, routing tables that represent the underlying physical structure well
can achieve increased performance. For this reason, the proposed methods for
topology mismatch problem basically use different levels of proximity
information to optimize them towards this direction. The algorithms are here
categorised based the previous work done by \cite{CDHR2002,CDCR2002,RSS2002}.

@@

%###############################################################################
%###############################################################################
%###############################################################################
%       GEGRAPHIC LAYOUT
%###############################################################################
%###############################################################################
%###############################################################################

@@

\textit{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths, combining the landmark binning method and small
scale distance probes to reveal the proximity properties of the underlying
network to the overlay. %Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.
This global view of the
state is made available to all nodes in order to help them find the best way to
route their messages. \textit{Global Soft-State} operates in two main stages,
generation and use of the proximity information. For generating the proximity
information a hybrid approach is proposed, which uses landmark clustering as a
preprocessing step in order to select a number of potential nearest neighbour
candidates and then refine the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. For using
the proximity information, the algorithm chooses a different path from the
classic gossiping approaches for constructing and maintaining the overlay. It is
based on landmark clustering for strategic placement of proximity information on
the overlay enabling any node to access such information using a landmark number
that reflects its physical position in the network. For various logical
regions\footnote{This might be a high-order zone in the eCAN\cite{xu_ecan_2002}
context or a set of nodes sharing a particular prefix in overlays such as
Pastry.} maps of physical information are built and published where each node
may appear in a maximum of $log\left( N \right)$ such maps. To dynamically adapt
to changing network conditions, a node subscribes to relevant \emph{soft states}
that utilize a notification system in order to initialize any necessary
neighbour re-selection.

Maintaining several host states at different layers, makes any content migration
costly. Additionally, the method does not make any continuing effort to remap
the overlay structure after a node successfully joins, in order to adapt its
state to any condition change. Although this approach greatly reduces the
routing latency to far nodes, it is unable to dynamically identify nodes that
are close to routers and gateways in order to construct the secondary overlay.
Nevertheless, static recognition of such nodes is currently done based on BGP
reports and pre-chosen landmarks, sacrificing the self-organising attribute of
traditional DHTs.

%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multicast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighbourhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximatelly 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralised nature of DHTs and
% thus poorly scalling.
low
\end{tabular}
\end{center}

@@

The bootstrap phase of Mithos starts with a subset of existing members as the
first set of candidates, and while the iteratively closest nodes are detected by
probing the neighborhood, the candidate neighbor list is updated. In order to
avoid a local minima, Mithos probes all the neighbours within a two-hop distance
from the current minimum before concluding the process.

After finding its first neighbour, the newcomming peer is assigned an ID using
information gathered during the iterative neighbour selection phase. Virtual
coordinates are assigned to the newcomming peer by using the distances of two
closest nodes and their neighbours, so that Euclidean distances between the node
and all known hosts predict the network latency between them
\cite{cox_vivaldi_2004}. The benefit of these synthetic coordinates are that
they are explicitly used as the node's ID, and distance computations among nodes
can be done in ID space without requiring physical measurements.

The last step of the algorithm is the interconnection among neighbours. Mithos
uses a \emph{quadrant-based} mechanism according to which each node establishes
a link to the closest neighbour in each quadrant. During forwarding, the next
hop is performed towards a neighbour in the same quadrant as the final
destination. The newcoming node may not know of other neighbours in all
quadrants, therefore, the node first identifies neighbours in all quadrants
using a mechanism based on ideas similar to a perimeter walk\footnote{Used in
Greedy Perimeter Stateless Routing (GPSR) protocol.} and then improves the
results using parallel path processing by taking into account further geometric
properties of node relationships.

@@

%
% TODO: review this part
%
%In order to avoid local minima during neighbour detection, extensive probing
%  must be undertaken. In simulation, unfortunately, only very small-sized
% overlay topologies (of 200 to 1000 nodes) have been used and thus no safe
% conclusions can be made as for the behaviour of an extensively large,
% real-world p2p deployment of the scheme.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing comunication latency among peers but its
% efficience is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used througout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incrimental probing is applied in quadradants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organises the overlay into a tree-based hierarchy
with main focus on reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. The authors theoretically show
that in LAPTOP routing path length is bounded by $O(log_d N)$ and node joining
and leaving in the overlay network is bounded by $O\left( d log_d N \right)$
hops in a balanced overlay tree, where $N$ is the number of nodes, and $d$ is
the maximum degree of each node. LAPTOP implements the geographical layout
approach  and constructs its layout in a self-organizing and efficient fashion,
by estimating the round-trip times to a small number of nodes in the overlay
network in order to make them roughly aware of their physical distances among
them.

@@

%The protocol is based on four definitions.
%\begin{enumerate}
% \item The amplitude of all possible measured RTTs is devided into intervals.
%  Each node measures its distance to its parent and is assigned a label $L_i$
% where $i$ denotes the configurable RTT interval in which the measured distance
% falls into. A special kind of node, the root, is initially assigned the $L_1$
% label and maintains (as all $L_1$ nodes do) a list of other $L_1$ nodes in the
% overlay.
% \item Any node can have children with level lower than theirs, except an
%  $L_{max}$ node which can only have $L_{max}$ level children and only in the
% case when its parent has reached its maximum degree.
% \item Each node is assigned a dot-formated address (e.g 1.3.4). Each octet
% ranges from
% $1$ to $d$, where $d$ is the maximum degree of the nodes. The assignment
% process
% is done by appending a unique octet to the address of each nodes parent, while
% root node is assigned address $1$.
% \item For any descendant node $Y$ of a node $X$, the measured distance among
%  each other, must always be less than the lower bound of the RTT interval
% denoted by $X$'s label.
%\end{enumerate}
%

@@

%
%The newcommer $N$ locates the root node and the later responds with a list of
%  $L_1$ nodes. $N$ then probes each of the $L_1$ nodes in search for the
% closest one. If the measured RTT to the closest $L_1$ falls into the first
% interval then the newcommer becomes a $L_1$ node as well. Otherwise node $N$
% sets the closest $L_1$ node as its potential parent node. This potential
% parent becomes the actual parent if it does not have any other children. If it
% has, $N$ gets a list of these $L_i$ nodes and by measuring the RTT to each of
% them tries to spot a new potential parent in order to repeat the above
% process.
%

% At join process the newcomming node is assigned its level label as well as its
% address by its parent node. Additionally, it initializes its routing table
%(with normal and caching entries) as it traverses the overlay in search for
%its parent node.  During a graceful departure, the referred node checks for
%children in the overlay. If it does not have any, it simply notifies its
%parent and leaves. If it has, it selects the child node with the lowest
%round-trip time to it in order to take its place so that the locality
%property is preserved. On the other hand, in the case of an arbitrary
%failure, after the children of the failed node detect their parent's absence
%(throught the aformentioned heartbeat mechanism), they start emmiting special
%messages to their grandparent node (the address of which is stored during
%join process}. In case of no response from the grandparent node, the children
%invoke the joining process to detect their new parent node.The parent of the
%failed node, aggregates the notifications from the above children nodes for a
%period of time, and then chooses the one with the lowest level label as the
%takeover node. Potential ties are broken by favouring the lower RTT. The
%parent of the failed node, finally informs accordingly all the children about
%the change in the hierarchy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: HERE STRUCTURED LANDMARK BINING APPROCH LIES
%
%Assuming a structured approach based on CAN\cite{ratnasamy_can_2001} and $m$
% landmark nodes. The coordinate space is then partitioned into $m!$ equally
%sized portions, each corresonding to a single ordering of the landmarks. To do
%this, the first dimension is divided into $m$ areas each of which is furtherly
%divided (second dimension) into $m - 1$ sections and so on. Having set this $m$
%dimensional space, at joining time, a node measures the delay to the set of
%landmarks in order to determine its associated bin and thus position itself in
%that portion of the coordinate space associated with its landmark ordering.
%Even though this scheme can
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It minimises routing length, but may suffer load imbalance since nodes higher
% in the tree hierarchy are more likely to route most of the messages in the
% overlay.
medium &
% Heartbeat approach incurs extra control overhead to the network. Fortunatelly
% involves only the parent and the children of the departing/failing node.
% nodes.
low &
% Seems to scale nicely from 10K- to 1M-node testbeds.
high
\end{tabular}
\end{center}

@@

\emph{Proximity in Kademlia} \cite{KLKP2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distingushes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimisation. One falling into
{\em proximity routing} and the other on {\em proximity neighbour selection}
approaches overlay optimization techiques for exploiting proximity. For the
first, the goal is in choosing the best next hop during routing a message. Due
to the fact that the routing in Kademlia is iterative, it is the initiator of
the lookup that chooses each next hop from a set of candidate nodes. Standard
Kedemlia always chooses the closest node with respect to the XOR metric but with
proximity routing selection, Kademlia chooses the one with the smallest underlay
metric cost. Thus, as in all such approaches, there is a trade-off between the
overlay and underlay distances.

Toward the enhancement of traffic locality, the authors also use information
from the MaxMind GeoIP database\footnote{MaxMind Geolocation Technology.
http://www.maxmind.com} to retrieve proximity information of a given peer based
on its region, country, or ISP location, and use this information to form
clusters of nearby peers. An alternative method could also be the use of Vivaldi
coordinates \cite{cox_vivaldi_2004}. However, authors report that clustering
approach performs better than Vivaldi protocol based on their experiments.
Authors also report that {\em Proximity routing} protocol successfully worked
with the Kademlia protocol and improved the locality of the connections over
peers.

As already mentioned the paper proposes \emph{proximity neighbour selection}
method, as well, for overlay optimisation. The goal, according to this, is to
keep peers with the least contact cost in the routing table. As Kademlia
constantly learns new peers (incoming requests, through iterative lookup) no
special algorithm for searching more cost effective peers is necessary and
simply choose the best peers seen so far.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{MT2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord, CHOP6 uses a finger table, whose entries hold more than
one candidate node.

%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it posseses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with propability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{SLCGZ2008} uses traceroute logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the traceroute to initialize the
centroinds of two sets. Then the peer calculates, for all hops allong its
tracerouted path, the absolute distance to these centroids of both sets and
assigns the routers to that centroid with which it has the smaller absolute
distance. After that, the mean and variance values are calculated and if the
variance is larger than a predefined threshold then the algorithm sets the two
latency mean values as new centroids for the two sets and loops again.
Ultimately peer will end up with two sets having the minimum intra-set variance.
The peer, then, chooses the router from the second set with the minimum hops
attribute and sets it as a threshold. The selected router and all others whose
hops attribute is larger than the threshold are classified as \emph{remote}
router cluster. The remaining are classified as \emph{near}. From the near
class, the peer chooses the one with maximum hops attribute as its edge router,
and registers it along with the all the near cluster into the DHT of the P2P
overlay. As new peers join the network, those that share the same edge router
or any of the members of the near router clustersm there would gather to form a
close peer cluster. As Edge routers can provide more valuable information than
other members of the near set, T2MC was designed to prioritize interaction of
peers and edge gateways.

%
% TODO: SOME DISCUSSION
%
%The use of Traceroute as a tool for implementing the distance measuring
%infrastructure raise concearns about its efficiency and scalability. Being,
%primarilly, a network diagnostic utility,
% Even though traceroute provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% traceroute is a very heavy tool and thus incurs excessive burden to the
% network resourses.
high &
% Traceroute is categorised as too heavy-weighted and intrucive for use in a
% larger scale system \cite{RHMKS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
\end{center}

>>>>

This section focuses on the structured P2P architectures. The following
paragraphs contain a thorough discussion and analysis of the algorithms proposed
in the literature for dealing with the topology mismatch problem in such
architectures. In structured P2P systems, the construction of the routing tables
in every participating node determines the efficiency of message forwarding.
Therefore, routing tables that represent the underlying physical structure well
can achieve increased performance. For this reason, the proposed methods for
topology mismatch problem basically use different levels of proximity
information to optimize them towards this direction. The algorithms are here
categorized based on the previous work done by \cite{CDHR2002,CDCR2002,RSS2002}.

@@

%###############################################################################
%###############################################################################
%###############################################################################
%       GEOGRAPHIC LAYOUT
%###############################################################################
%###############################################################################
%###############################################################################

@@

\textit{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths, combining the landmark binning method and small
scale distance probes to reveal the proximity properties of the underlying
network to the overlay. %Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.
This global view of the
state is made available to all nodes in order to help them find the best way to
route their messages. \textit{Global Soft-State} operates in two main stages,
generation and use of the proximity information. For generating the proximity
information a hybrid approach is proposed, which uses landmark clustering as a
preprocessing step in order to select a number of potential nearest neighbor
candidates and then refine the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. For using
the proximity information, the algorithm chooses a different path from the
classic gossiping approaches for constructing and maintaining the overlay. It is
based on landmark clustering for strategic placement of proximity information on
the overlay enabling any node to access such information using a landmark number
that reflects its physical position in the network. For various logical
regions\footnote{This might be a high-order zone in the eCAN\cite{xu_ecan_2002}
context or a set of nodes sharing a particular prefix in overlays such as
Pastry\cite{antony_pastry_2001}.} maps of physical information are built and
published where each node may appear in a maximum of $log\left( N \right)$ such
maps. To dynamically adapt to changing network conditions, a node subscribes to
relevant \emph{soft states} that utilize a notification system in order to
initialize any necessary neighbor re-selection.

Maintaining several host states at different layers, makes any content migration
costly. Additionally, the method does not make any continuing effort to remap
the overlay structure after a node successfully joins, in order to adapt its
state to any condition change. Although this approach greatly reduces the
routing latency to far nodes, it is unable to dynamically identify nodes that
are close to routers and gateways in order to construct the secondary overlay.
Nevertheless, static recognition of such nodes is currently done based on BGP
reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
traditional DHTs.

%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling.
low
\end{tabular}
\end{center}

@@

The bootstrap phase of Mithos starts with a subset of existing members as the
first set of candidates, and while the iteratively closest nodes are detected by
probing the neighborhood, the candidate neighbor list is updated. In order to
avoid a local minima, Mithos probes all the neighbors within a two-hop distance
from the current minimum before concluding the process.

After finding its first neighbor, the new coming peer is assigned an ID using
information gathered during the iterative neighbor selection phase. Virtual
coordinates are assigned to the new coming peer by using the distances of two
closest nodes and their neighbors, so that Euclidean distances between the node
and all known hosts predict the network latency between them
\cite{cox_vivaldi_2004}. The benefit of these synthetic coordinates are that
they are explicitly used as the node's ID, and distance computations among nodes
can be done in ID space without requiring physical measurements.

The last step of the algorithm is the interconnection among neighbors. Mithos
uses a \emph{quadrant-based} mechanism according to which each node establishes
a link to the closest neighbor in each quadrant. During forwarding, the next
hop is performed towards a neighbor in the same quadrant as the final
destination. The new coming node may not know of other neighbors in all
quadrants, therefore, the node first identifies neighbors in all quadrants
using a mechanism based on ideas similar to a perimeter walk\footnote{Used in
Greedy Perimeter Stateless Routing (GPSR) protocol.} and then improves the
results using parallel path processing by taking into account further geometric
properties of node relationships.

@@

%
% TODO: review this part
%
%In order to avoid local minima during neighbor detection, extensive probing
%  must be undertaken. In simulation, unfortunately, only very small-sized
% overlay topologies (of 200 to 1000 nodes) have been used and thus no safe
% conclusions can be made as for the behavior of an extensively large,
% real-world p2p deployment of the scheme.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organizes the overlay into a tree-based hierarchy
with main focus on reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. The authors theoretically show
that in LAPTOP routing path length is bounded by $O(log_d N)$ and node joining
and leaving in the overlay network is bounded by $O\left( d log_d N \right)$
hops in a balanced overlay tree, where $N$ is the number of nodes, and $d$ is
the maximum degree of each node. LAPTOP implements the geographical layout
approach  and constructs its layout in a self-organizing and efficient fashion,
by estimating the round-trip times to a small number of nodes in the overlay
network in order to make them roughly aware of their physical distances among
them.

@@

%The protocol is based on four definitions.
%\begin{enumerate}
% \item The amplitude of all possible measured RTTs is divided into intervals.
%  Each node measures its distance to its parent and is assigned a label $L_i$
% where $i$ denotes the configurable RTT interval in which the measured distance
% falls into. A special kind of node, the root, is initially assigned the $L_1$
% label and maintains (as all $L_1$ nodes do) a list of other $L_1$ nodes in the
% overlay.
% \item Any node can have children with level lower than theirs, except an
%  $L_{max}$ node which can only have $L_{max}$ level children and only in the
% case when its parent has reached its maximum degree.
% \item Each node is assigned a dot-formated address (e.g 1.3.4). Each octet
% ranges from
% $1$ to $d$, where $d$ is the maximum degree of the nodes. The assignment
% process
% is done by appending a unique octet to the address of each nodes parent, while
% root node is assigned address $1$.
% \item For any descendant node $Y$ of a node $X$, the measured distance among
%  each other, must always be less than the lower bound of the RTT interval
% denoted by $X$'s label.
%\end{enumerate}
%

@@

%
%The new comer $N$ locates the root node and the later responds with a list of
%  $L_1$ nodes. $N$ then probes each of the $L_1$ nodes in search for the
% closest one. If the measured RTT to the closest $L_1$ falls into the first
% interval then the new comer becomes a $L_1$ node as well. Otherwise node $N$
% sets the closest $L_1$ node as its potential parent node. This potential
% parent becomes the actual parent if it does not have any other children. If it
% has, $N$ gets a list of these $L_i$ nodes and by measuring the RTT to each of
% them tries to spot a new potential parent in order to repeat the above
% process.
%

% At join process the new coming node is assigned its level label as well as its
% address by its parent node. Additionally, it initializes its routing table
%(with normal and caching entries) as it traverses the overlay in search for
%its parent node.  During a graceful departure, the referred node checks for
%children in the overlay. If it does not have any, it simply notifies its
%parent and leaves. If it has, it selects the child node with the lowest
%round-trip time to it in order to take its place so that the locality
%property is preserved. On the other hand, in the case of an arbitrary
%failure, after the children of the failed node detect their parent's absence
%(through the aforementioned heartbeat mechanism), they start emitting special
%messages to their grandparent node (the address of which is stored during
%join process}. In case of no response from the grandparent node, the children
%invoke the joining process to detect their new parent node.The parent of the
%failed node, aggregates the notifications from the above children nodes for a
%period of time, and then chooses the one with the lowest level label as the
%takeover node. Potential ties are broken by favoring the lower RTT. The
%parent of the failed node, finally informs accordingly all the children about
%the change in the hierarchy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: HERE STRUCTURED LANDMARK BINNING APPROACH LIES
%
%Assuming a structured approach based on CAN\cite{ratnasamy_can_2001} and $m$
% landmark nodes. The coordinate space is then partitioned into $m!$ equally
%sized portions, each corresponding to a single ordering of the landmarks. To do
%this, the first dimension is divided into $m$ areas each of which is further
%divided (second dimension) into $m - 1$ sections and so on. Having set this $m$
%dimensional space, at joining time, a node measures the delay to the set of
%landmarks in order to determine its associated bin and thus position itself in
%that portion of the coordinate space associated with its landmark ordering.
%Even though this scheme can
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It minimizes routing length, but may suffer load imbalance since nodes higher
% in the tree hierarchy are more likely to route most of the messages in the
% overlay.
medium &
% Heartbeat approach incurs extra control overhead to the network. Fortunately
% involves only the parent and the children of the departing/failing node.
% nodes.
low &
% Seems to scale nicely from 10K- to 1M-node testbeds.
high
\end{tabular}
\end{center}

@@

\emph{Proximity in Kademlia} \cite{KLKP2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment, in order to
optimize the underlying network usage of the protocol. The work in this paper
can also be considered, as a more generic study over building proximity in the
context of iterative lookup algorithms. Focus is given on both the overlay and
the underlaying tiers in the sense that in the first improves the routing
performance according to a cost metric that is provided by the later and
quantifies the suitability of establishing a communication link between peers as
a cost function, based on the used proximity criteria (RTT, ISP locality, etc.).
%An underlay metric provides information about the underlay network. The paper
%  distinguishes between three kinds of possibilities to quantify it:
%\begin{itemize}
% \item Using measurements gained by previous lookups
% \item Using measurements acquired by other peers or jointly calculated with
%  others
% \item Using a local database to look up information
%\end{itemize}
The paper proposes two approaches for overlay optimization. One falling into
{\em proximity routing} and the other on {\em proximity neighbor selection}
approaches overlay optimization techniques for exploiting proximity. For the
first, the goal is in choosing the best next hop during routing a message. Due
to the fact that the routing in Kademlia is iterative, it is the initiator of
the lookup that chooses each next hop from a set of candidate nodes. Standard
Kademlia always chooses the closest node with respect to the XOR metric but with
proximity routing selection, Kademlia chooses the one with the smallest underlay
metric cost. Thus, as in all such approaches, there is a trade-off between the
overlay and underlay distances.

Towards the enhancement of traffic locality, the authors also use information
from the MaxMind GeoIP database\footnote{MaxMind Geolocation Technology.
http://www.maxmind.com} to retrieve proximity information of a given peer based
on its region, country, or ISP location, and use this information to form
clusters of nearby peers. An alternative method could also be the use of Vivaldi
coordinates \cite{cox_vivaldi_2004}. However, authors report that clustering
approach performs better than Vivaldi protocol based on their experiments.
Authors also report that {\em Proximity routing} protocol successfully worked
with the Kademlia protocol and improved the locality of the connections over
peers.

As already mentioned the paper proposes \emph{proximity neighbor selection}
method, as well, for overlay optimization. The goal, according to this, is to
keep peers with the least contact cost in the routing table. As Kademlia
constantly learns new peers (incoming requests, through iterative lookup) no
special algorithm for searching more cost effective peers is necessary and
simply choose the best peers seen so far.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CHOord considering Proximity on IPv6 (CHOP6)}
\emph{CHOP6} \cite{MT2007} roughly estimates the proximity among
nodes by exploiting the IPv6 address format and RTT information if available.
The proximity estimation is achieved by introducing a 64-bit ID scheme in which
the least significant bit part is the IPv6 global routing prefix and thus
enabling a longest prefix match scheme. The protocol is designed based on the
observation that it is possible to estimate a node's geographical location by
simply examining the upper 32-bits of its IPv6 address. Moreover, similar to
Chord\cite{stoica_chord_2001}, CHOP6 uses a finger table, whose entries hold
more than one candidate node.

%
%\paragraph{}
% There are three cases in which a node chooses the next hop according to
% information it possesses.
%\begin{itemize}
% \item When no information about RTT is available candidate next hops, the
%  sender just selects a node in the finger table entry which shares the longest
% prefix with the destination.
% \item There is another possibility that after some communication with other
%  nodes, the source node should know of the RTTs to some of the nodes in finger
% table entry. In this case, the source node chooses the one with the smallest
% RTT with probability $p$. If there is a node with no measured RTT then the
% sender can select such a node with probability $1 - p$
% \item In this last case the source node has already communicated with all
%  candidate node in the finger table entry. Thus, the node selects the node
% whose RTT is the smallest with probability $p$, the one with the second
% smallest with probability $q$ and so on, where $0 \leq \ldots < r < q < p < 1$
% and $p+q+r+\ldots \leq 1$
%\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{T2MC}
T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
systems and cluster close by peers, thus reducing redundant traffic that crosses
autonomous system boundaries. T2MC uses a customized k-mean classification
algorithm with $k=2$ to perform the classification, and exploits the stable
structure of the Internet routers to guide clustering. The peer chooses the
minimum and maximum Latency results from the trace-route to initialize the
centroids of two sets. Then the peer calculates, for all hops along its
trace-routed path, the peer calculates the absolute distance to these centroids
of both sets and assigns the routers to that centroid with which it has the
smaller absolute distance. After that, the mean and variance values are
calculated and if the variance is larger than a predefined threshold then the
algorithm sets the two latency mean values as new centroids for the two sets and
loops again. Ultimately peer will end up with two sets having the minimum
intra-set variance. The peer, then, chooses the router from the second set with
the minimum hops attribute and sets it as a threshold. The selected router and
all others whose hops attribute is larger than the threshold are classified as
\emph{remote} router cluster. The remaining are classified as \emph{near}. From
the near class, the peer chooses the one with maximum hops attribute as its edge
router, and registers it along with all near clusters into the DHT of the
P2P overlay. As new peers join the network, those that share the same edge
router or any of the members of the near router clusters, would form a close
peer cluster. As Edge routers can provide more valuable information than other
members of the near set, T2MC was designed to prioritize interaction of peers
and edge gateways.

%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RHMKS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
\end{center}
